Why aren't significance tests commonly used for linear regression diagnostics?

### 2022-09-04 paper_comparison/paper_comparison/paper_comparison.Rmd
update residual departure

Graphical summaries in which residuals are plotted against fitted values or other functions of the predictor variables that are approximately orthogonal to residuals are referred to as standard residual plots in @cook1982residuals. As suggested by @cook1982residuals, these kinds of diagnostic plots are commonly used to identify patterns that are indicative of non-linearity or nonconstant error variance.

Raw residuals and studentized residuals are the two most frequently used residuals in standard residual plots. The debt on which type of residuals should be used is always present. While raw residuals are the most common computer regression software package output, by applying a scaling factor, the ability to reveal nonconstant error variance in standard residual plots will often be enhanced by studentized residuals in small sample size [@gunst1980regression]. As a two-dimensional representation of a model in a $p$-dimensional space, standard residual plots project data points onto the variable of the horizontal axis, which is a vector in $p$-dimensional space. Observations with the same projection will be treated as equivalent as they have the same abscissa. Consequently, standard residual plots are often useful in revealing model inadequacies in the direction of the variable of the horizontal axis but could be inadequate for detecting patterns in other directions, especially in those perpendicular to the variable of the horizontal axis. Hence, in practice, multiple standard residual plots with different horizontal axes will be examined [@cook1982residuals]. Overlapping data points is another general issue in scatter plots not limited to standard residual plots, which often makes plots difficult to interpret because visual patterns are concealed. Thus, for a relatively large sample size, @cleveland1975graphical suggests the use of robust moving statistics as reference lines to give aid to the eye in seeing patterns, which nowadays, are usually replaced with a spline or local polynomial regression line.

Other types of data plots that are often used in regression diagnostics include partial residual plots and probability plots. Partial residual plots are useful supplements to standard residual plots as they provide additional information on the extent of the non-linearity. Probability plots can be used to compare the sampling distribution of the residuals to the normal distribution for assessing the normality assumptions.

>>>>

Graphical summaries in which residuals are plotted against fitted values or other functions of the predictor variables that are approximately orthogonal to residuals are referred to as standard residual plots in @cook1982residuals. As shown in Figure [ref here], the top-left panel is a good residual plot with residuals evenly distributed at both sides of the horizontal zero line showing no noticeable patterns.

There are many departures from a good residual plot, but we will consider only three types of them in this paper, which are also the most commonly checked departures for a residual plot. The first one is non-linearity. Any unnatural non-linear curve presented in the residual plot could be considered an indicative of non-linearity. At the top-right of Figure [ref here], there is an example residual plot of this type of departure. The second type of departure  we will consider is heterskedasticity. The usual pattern of this type of departure is the inconsistent distribution of the residuals for different x values. Visually, it usually results in the so-called "butterfly" shape as shown in the bottom-left panel of Figure [ref here], or the "triangle" shape where the smallest variance occurs at the edges of the x-axis. The last type of departure is non-normality. This departure is usually harder to be detected from the residuals plot compared to non-linearity and heterskedasticity. In most the case, a quantile-quantile plot can do a better job. Depending on the actual distribution of the residuals, different visual patterns will be discovered. If the distribution is skewed, one will see some outliers presented on only one side of the zero line as shown in the bottom-right of Figure [ref here].

<!-- Raw residuals and studentized residuals are the two most frequently used residuals in standard residual plots. The debt on which type of residuals should be used is always present. While raw residuals are the most common computer regression software package output, by applying a scaling factor, the ability to reveal nonconstant error variance in standard residual plots will often be enhanced by studentized residuals in small sample size [@gunst1980regression]. As a two-dimensional representation of a model in a $p$-dimensional space, standard residual plots project data points onto the variable of the horizontal axis, which is a vector in $p$-dimensional space. Observations with the same projection will be treated as equivalent as they have the same abscissa. Consequently, standard residual plots are often useful in revealing model inadequacies in the direction of the variable of the horizontal axis but could be inadequate for detecting patterns in other directions, especially in those perpendicular to the variable of the horizontal axis. Hence, in practice, multiple standard residual plots with different horizontal axes will be examined [@cook1982residuals]. Overlapping data points is another general issue in scatter plots not limited to standard residual plots, which often makes plots difficult to interpret because visual patterns are concealed. Thus, for a relatively large sample size, @cleveland1975graphical suggests the use of robust moving statistics as reference lines to give aid to the eye in seeing patterns, which nowadays, are usually replaced with a spline or local polynomial regression line.  -->

<!-- Other types of data plots that are often used in regression diagnostics include partial residual plots and probability plots. Partial residual plots are useful supplements to standard residual plots as they provide additional information on the extent of the non-linearity. Probability plots can be used to compare the sampling distribution of the residuals to the normal distribution for assessing the normality assumptions. -->

### 2022-09-04 paper_comparison/paper_comparison/paper_comparison.tex
update residual departure

Graphical summaries in which residuals are plotted against fitted values
or other functions of the predictor variables that are approximately
orthogonal to residuals are referred to as standard residual plots in
\citet{cook1982residuals}. As suggested by \citet{cook1982residuals},
these kinds of diagnostic plots are commonly used to identify patterns
that are indicative of non-linearity or nonconstant error variance.

Raw residuals and studentized residuals are the two most frequently used
residuals in standard residual plots. The debt on which type of
residuals should be used is always present. While raw residuals are the
most common computer regression software package output, by applying a
scaling factor, the ability to reveal nonconstant error variance in
standard residual plots will often be enhanced by studentized residuals
in small sample size \citep{gunst1980regression}. As a two-dimensional
representation of a model in a \(p\)-dimensional space, standard
residual plots project data points onto the variable of the horizontal
axis, which is a vector in \(p\)-dimensional space. Observations with
the same projection will be treated as equivalent as they have the same
abscissa. Consequently, standard residual plots are often useful in
revealing model inadequacies in the direction of the variable of the
horizontal axis but could be inadequate for detecting patterns in other
directions, especially in those perpendicular to the variable of the
horizontal axis. Hence, in practice, multiple standard residual plots
with different horizontal axes will be examined
\citep{cook1982residuals}. Overlapping data points is another general
issue in scatter plots not limited to standard residual plots, which
often makes plots difficult to interpret because visual patterns are
concealed. Thus, for a relatively large sample size,
\citet{cleveland1975graphical} suggests the use of robust moving
statistics as reference lines to give aid to the eye in seeing patterns,
which nowadays, are usually replaced with a spline or local polynomial
regression line.

Other types of data plots that are often used in regression diagnostics
include partial residual plots and probability plots. Partial residual
plots are useful supplements to standard residual plots as they provide
additional information on the extent of the non-linearity. Probability
plots can be used to compare the sampling distribution of the residuals
to the normal distribution for assessing the normality assumptions.

>>>>

Graphical summaries in which residuals are plotted against fitted values
or other functions of the predictor variables that are approximately
orthogonal to residuals are referred to as standard residual plots in
\citet{cook1982residuals}. As shown in Figure {[}ref here{]}, the
top-left panel is a good residual plot with residuals evenly distributed
at both sides of the horizontal zero line showing no noticeable
patterns.

There are many departures from a good residual plot, but we will
consider only three types of them in this paper, which are also the most
commonly checked departures for a residual plot. The first one is
non-linearity. Any unnatural non-linear curve presented in the residual
plot could be considered an indicative of non-linearity. At the
top-right of Figure {[}ref here{]}, there is an example residual plot of
this type of departure. The second type of departure we will consider is
heterskedasticity. The usual pattern of this type of departure is the
inconsistent distribution of the residuals for different x values.
Visually, it usually results in the so-called ``butterfly'' shape as
shown in the bottom-left panel of Figure {[}ref here{]}, or the
``triangle'' shape where the smallest variance occurs at the edges of
the x-axis. The last type of departure is non-normality. This departure
is usually harder to be detected from the residuals plot compared to
non-linearity and heterskedasticity. In most the case, a
quantile-quantile plot can do a better job. Depending on the actual
distribution of the residuals, different visual patterns will be
discovered. If the distribution is skewed, one will see some outliers
presented on only one side of the zero line as shown in the bottom-right
of Figure {[}ref here{]}.
